Estimating associations between childhood exposure to non-persistent endocrine disruptors, corticosteroids, and neurodevelopment: A study based on the parametric g-formula

### 2023-12-20 output/paper/manuscript.qmd
Nothing.

Figures [-@fig-marginal-2-cortisolprod; -@fig-marginal-2-cortisoneprod; -@fig-marginal-2-corticosteroneprod; -@fig-marginal-2-11b] present the forest plots for the marginal effects of the non-persistent \acr{edcs} on cortisol production, cortisone production, corticosterone production, and 11bHSD activity, respectively.

>>>>

@Fig-marginal-2 presents the forest plot for the marginal effects of the non-persistent \acr{edcs} on cortisol production, cortisone production, corticosterone production, and 11bHSD activity, respectively.
